Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey

### 2021-11-13 code/analysis_code/analysisscript.Rmd
Manuscript Updated!

---
title: "analysis"
author: "Ehsan"
date: "10/27/2021"
output: html_document
---

@@

#we want to predict each infection status level, not a single contrast. It was a bit difficult to figure out how to do this, but one needs to search here for the model to find the function one needs, turns out it is called multinom_reg()

@@

#metrics of training data
```{r}
collect_metrics(training_data_fit)
```
##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds with test data
```{r}
mydata_folds2 <- vfold_cv(test_data, v = 5, repeats =5, strata= "infection_status_info")
```
#fitting the test data
```{r}
test_data_fit <- 
 mydata_wf %>% 
  fit_resamples(mydata_folds2)
```

#metrics of test data
```{r}
collect_metrics(test_data_fit)
```

>>>>

---
title: "analysis"
author: "Ehsan"
date: "11/12/2021"
output: html_document
---

@@

#saved it as a file
```{r}
summarytable_file18 = here("results", "Comparison of Models.rds")
saveRDS(compare_log_model, file = summarytable_file18)
```
#we want to predict each infection status level, not a single contrast. It was a bit difficult to figure out how to do this, but one needs to search here for the model to find the function one needs, turns out it is called multinom_reg()

@@

#metrics of training data
```{r}
training_data_metrics <- collect_metrics(training_data_fit)
training_data_metrics
```
#saved it as a file
```{r}
summarytable_file19 = here("results", "Metrices of Training Data.rds")
saveRDS(training_data_metrics, file = summarytable_file19)
```

##5-fold cross validation, 5 times repeated, stratified on `infection status` for the CV folds with test data
```{r}
mydata_folds2 <- vfold_cv(test_data, v = 5, repeats =5, strata= "infection_status_info")
```
#fitting the test data
```{r}
test_data_fit <- 
 mydata_wf %>% 
  fit_resamples(mydata_folds2)
```

#metrics of test data
```{r}
test_data_metrics <- collect_metrics(test_data_fit)
test_data_metrics
```
#saved it as a file
```{r}
summarytable_file20 = here("results", "Metrices of TestData.rds")
saveRDS(test_data_metrics, file = summarytable_file20)
```

### 2021-11-13 products/manuscript/Manuscript.Rmd
Manuscript Updated!

>>>>

The comparison between these three models give us this information:

```{r summarytable18,  echo=FALSE}
resulttable=readRDS("../../results/Comparison of Models.rds")
knitr::kable(resulttable, caption = "Comparison of the Models")
```

we want to predict each infection status level, not a single contrast by using multinom_reg(). The result is as following:

```{r summarytable19,  echo=FALSE}
resulttable=readRDS("../../results/Metrices of Training Data.rds")
knitr::kable(resulttable, caption = "Metrices of Training Data")
```

```{r summarytable20,  echo=FALSE}
resulttable=readRDS("../../results/Metrices of TestData.rds")
knitr::kable(resulttable, caption = "Metrices of Testing Data")
```
